Optimal (Multiway) Spatial Joins

### 2024-06-06 msj.tex
yufei

In the {\em reporting version} of Problem $\mathscr{A}$, the goal is to output, for each point $p \in P$, all the rectangles $r \in R$ containing $p$. In Figure~\ref{fig:guard}a, for instance, the output is $\set{(p_1, \emptyset), (p_2: r_1, r_2), (p_3: r_2)}$. As shown in Appendix~\ref{app:bricks}, The problem can be solved in $O(n \log n + \out)$ time, where $\out$ is the number of pairs $(p, r) \in P \times R$ such that $p \in r$.

>>>>

In the {\em reporting version} of Problem $\mathscr{A}$, the goal is to output, for each point $p \in P$, all the rectangles $r \in R$ containing $p$; if no such $r$ exists, report nothing for $p$. In Figure~\ref{fig:guard}a, for instance, the output is $\set{(p_2: r_1, r_2), (p_3: r_2)}$. As shown in Appendix~\ref{app:bricks}, The problem can be solved in $O(n \log n + \out)$ time, where $\out$ is the number of pairs $(p, r) \in P \times R$ such that $p \in r$.
